---
title: "Task2_Studentdata"
author: "Bhagyashree Khabale"
date: "09/09/2020"
output: html_document
---

Simple Linear Regression:Predicting the Scores w.r.t. No of Hours

**Step1:
Importing Student dataset into.csv file and Check the structure of the dataset**

```{r}
Student <- read.csv("~/Student.txt")
str(Student)
summary(Student)
```

**Step2:
Importing library for Regression**

```{r}
library(caTools)
set.seed(2)
split=sample.split(Student,SplitRatio = 0.7)
train=subset(Student,split="True")
test=subset(Student,split="False")
```
*data has been divided into two part i.e. test and train for the prediction so data split randomly with the help of set.seed command by giving a splitratio so here in this dataset 70 % data went to train set 
and 20 % went to test set*


**Step3:
Creating Regression model (y=Scores,x=Hours)**

```{r}
model=lm(Scores~Hours,data = train)
summary(model)
```

**Step4:
Checking the Actual and predicted Score value **

```{r}
predict_result=predict(model,test)
result=cbind(test,predict_result)
result
```

This model gives  95% accuracy which means 5% is not predicted correctly 

**Step5:
Creating a Scatter plot to see the scatter data of Scores and Hours**

#Define Dependent and Independent Variable

```{r}
library(ggplot2)
y=Student$Scores
x=Student$Hours
plot(x,y,ylab = "Scores",xlab = "No.of Hours",main = "Scores vs Hours")
```

**Step6:
Plotting Best fit line**

```{r}
library(ggplot2)
plot(x,y,ylab = "Scores",xlab = "No.of Hours",main = "Scores vs Hours")
abline(lm(y~x))
```

**Step7:
Accuracy of the Model**

#Calculating Sum of Error of Square

```{r}
SSE=sum((test$Scores-predict_result)^2)
SSE
```

#calculating Total sum of square of Error
```{r}
SST=sum((test$Scores-mean(Student$Scores))^2)
SST
```

#Calculating Rss value
```{r}
r=1-(SSE/SST)
r
```


**Output**

Accuracy of the Model is:**95.29%**

For 9.2 hours prdicted Score will be **92.42%**
